\bf Supplementary Material

### 2025-09-23 manuscript/reply2.tex
described investigation in reply letter

The revised manuscript incorporates the following notable change:
\begin{enumerate}
\item A supplement has been added, which includes both
our previous exploration of automatic block size selection as
well as our new simulations for block bootstrap under
\citet{babu2004goodness}'s bias correction.
\end{enumerate}

@@

@@

Thank you for the suggestion, these investigations have now been placed in a supplement, and they are still referred to in
the main manuscript.

@@

Thank you for pointing this out. It has been
corrected to "average empirical distribution function" in the manuscript.

>>>>

The revised manuscript includes one notable change:
\begin{enumerate}
\item A supplement has been added, which includes both
our previous exploration of automatic block size selection as
well as our new simulations for block bootstrap under
\citet{babu2004goodness}'s bias correction.
\end{enumerate}

@@

We thank the AE for this helpful comment. We have added a supplement
which includes a section on "Performance of Nonparametric
Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness} Bias Correction". We re-ran the simulation study from the main
manuscript, but we replaced the $K_n(x)$ bias correction with $C_n(x)$.
The results are discussed in the supplement, and are alluded to in the main paper. Overall,
we find that there is no noticeable improvement in either size
or power when using the $K_n(x)$ bias correction, even for small sample
sizes. With these results, we recommend ........

@@

Thank you for the suggestion, these investigations have now been placed in the "Performance of Nonparametric
Block Bootstrap Kolmogorov-Smirnov Test with Block Size Calibration" of
the new supplement, and they are still referred to in
the main manuscript.

@@

Thank you for pointing this out. This typo has been
corrected to "average empirical distribution function" in the manuscript.
